The 32nd Intelligent Ground Vehicle Competition (IGVC) is an event hosted at Oakland University in Rochester, Michigan, on May 30th to June 2nd, 2025. This competition offers students the unique and challenging opportunity to develop autonomous ground vehicles. Through this competition, students will gain hands on experience with the latest industry relevant technologies, including robotics, artificial intelligence, etc., and enhance their overall technical skills. Furthermore, this competition fosters an environment for students that encourages collaboration, creativity, and other essential soft skills.

Currently, the field of autonomous ground vehicles is experiencing rapid growth in today's technology driven world.
Employers may search specifically for students who have experience with AI, robotics, etc. However, current educational programs may not properly equip students with the practical skills necessary to succeed in this industry, therefore leaving them unprepared for the real challenges faced in the workplace.

The IGVC offers a solution to this issue by creating an environment that simulates the development process of autonomous ground vehicles. Here, by building autonomous ground vehicles, students will apply the knowledge they have gained from academics, while also gaining hands on experience with various fields from software engineering to computer and hardware engineering. Additionally, by working with constraints in deadlines and budgets, students will be better prepared for industry conditions and workflow.

The IGVC offers several benefits to sponsors and customers. Sponsors who provide students hardware to the teams will cultivate a pool of future engineers who already have experience working with their hardware and technology. For companies looking to hire new talent, the competition offers them a chance to observe the teams in action, creating potential recruitment opportunities for students and fostering industry connections.

Ultimately, the IGVC helps to bridge the gap between academia and industry. The competition provides an environment where students can learn and improve the necessary technical and soft skills required to succeed in the industry, which complements the students academic curriculum. Thus, the IGVC is a valuable opportunity for both students and sponsors to facilitate creativity, experience, and networking.